Individual heterogeneity in the functional network topography of medial prefrontal

### 2019-09-06 Manuscript.Rmd
final revisions before sending to Joe/Sean

---
title: Individual heterogeneity in the functional network topography of medial prefrontal
  cortex
author: "Claudio Toro-Serey^1^, Sean M. Tobyne^2^, & Joseph T. McGuire^1^"
csl: apa.csl
output:
  word_document: #default
    reference_docx: Style_reference_draft.docx
  pdf_document:
    highlight: haddock
    keep_tex: no
header-includes:
- \usepackage{setspace}\doublespacing
- \usepackage[left]{lineno}
- \linenumbers
- \usepackage{float}
- \newcommand{\beginsupplement}{ \setcounter{table}{0} \renewcommand{\thetable}{S\arabic{table}}
  \setcounter{figure}{0} \renewcommand{\thefigure}{S\arabic{figure}} }
subtitle: 'Abbreviated Title: Heterogeneity in the functional topography of mPFC'
bibliography: mPFC_paper.bib
---

@@

## Significance Statement

  Multiple psychological functions engage topographically overlapping regions of human medial prefrontal cortex (mPFC), and the reason for the apparent overlap is not yet well understood. Here we present evidence that our understanding of the functional organization of mPFC can be advanced by accounting for individual-level topographic variability. We report results from a data-driven, network-based approach to subdividing mPFC and posterior cingulate cortex jointly into two distinct communities on the basis of non-task functional neuroimaging data. One of the identified communities corresponded to the brain's canonical default network. The community structure of mPFC was stable across test/re-test but exhibited high variability across individuals. The approach we introduce will help characterize the functional role of mPFC across diverse psychological domains.

@@

  The outline of our paper is as follows. First, we established a search space by selecting parcels from an established brain atlas [@Glasser2016] that corresponded to previously defined DN and limbic networks on the medial cortical wall [@Yeo2011]. A cortical surface-based meta-analysis of the DN and valuation literatures identified a parcel in PCC that was DN-specific at the aggregate level. We focused on the contrast between DN and valuation areas because of their notable overlap in mPFC and PCC, despite being segregable elsewhere in the brain [@Acikalin2017]. We then derived a functional connectivity network of all the surface vertices within the search space for each of `r length(dir(path = './Summary'))` individual resting-state fMRI data sets from the Human Connectome Project [HCP; @VanEssen2012], and used the SP algorithm to subdivide each individual's network into DN and non-DN communities (labeled according to which community included the meta-analytically identified DN-specific parcel in PCC). Focusing on individual vertices in the search space rather than the parcels (as is typical in brain network analyses) allowed us to finely delineate the topographic extent of each community. The resulting communities varied topographically across individuals, while also appearing to follow common organizational principles. Sliding window and test-retest analyses showed that these partitionings were highly similar across scanning days within (but not between) individuals, and that individual-level idiosyncrasy was greater in mPFC. Partitionings obtained from the SP algorithm had higher test-retest reliability than did analogous results from seed-based functional connectivity. We found that the DN community was likely to be located within principal sulci in ventral mPFC and left PCC, but in gyri within superior mPFC and right PCC. Lastly, we describe how the structure of the resulting automatically defined DN and non-DN communities both aligns with and differs from a recently proposed scheme for identifying subdivisions within the DN [@Braga2017; @Braga2019]. Our work highlights the usefulness of estimating brain effects at the individual level in mPFC and PCC, provides a new framework and tool set for future investigations of overlap across cognitive domains, and motivates future re-examination of seemingly inseparable cognitive processes (such as valuation and introspective thought) in these areas.

@@

Figure 2 shows a representative partitioning of the search space for a single participant (100307; additional examples are presented in the first two columns of Supplemental Figure 1). The SP algorithm subdivides a network according to the positive versus negative values in the Fiedler vector (the eigenvector related to the second-to-lowest eigenvalue of the network's normalized Laplacian matrix, see Methods). Since this is a data-driven approach, there is no a priori labeling for the two communities. We assigned the DN label to the community that contained the DN-specific PCC parcel from the meta-analysis (7m). We oriented each individual's Fiedler vector so positive values corresponded to the DN community [@Nenning2017], and were assigned a value of 1 in the binarized partitionings (with 0 denoting non-DN). In qualitative terms, the resulting patterns contained substantial DN coverage in posterior PCC (as dictated by our labeling strategy), with non-DN vertices in anterior PCC. The mPFC region tended to include DN vertices in its ventral-anterior and dorsal-anterior areas, with a persistent non-DN pocket between them. This non-DN section extended posteriorly into pregenual cinglate cortex (area a24).

@@

Figure 6 shows ARI ratios for PCC and mPFC. A signed-rank test showed evidence for specificity (i.e. ratios > 1) in both mPFC (median = `r round(median(Halves_RIRatios_PFC), digits = 2)`, IQR = `r round(quantile(Halves_RIRatios_PFC, 0.25), digits = 2)` - `r round(quantile(Halves_RIRatios_PFC, 0.75), digits = 2)`, V = `r Halves_PFC_ratioTest$statistic`, *p* `r ifelse(Halves_PFC_ratioTest$p.value < 0.001, "< 0.001", paste("=", Halves_PFC_ratioTest$p.value))`) and PCC (median = `r round(median(Halves_RIRatios_PCC), digits = 2)`, IQR = `r round(quantile(Halves_RIRatios_PCC, 0.25), digits = 2)` - `r round(quantile(Halves_RIRatios_PCC, 0.75), digits = 2)`, V = `r Halves_PCC_ratioTest$statistic`, *p* `r ifelse(Halves_PCC_ratioTest$p.value < 0.001, "< 0.001", paste("=", Halves_PCC_ratioTest$p.value))`). Moreover, the ratios for mPFC were significantly greater than those for PCC when compared with a paired permutation test (*p* `r ifelse(Halves_mPFCvPCC_permTest$Pval < 0.001, "< 0.001", paste("=", Halves_mPFCvPCC_permTest$Pval))`; Cohen's D = `r round(Halves_mPFCvPCC_ES, digits = 2)`). These test/retest results suggest that the topographic variability seen in mPFC arises at least in part from stable and subject-specific organizational patterns (examples of these partitionings can be found on Supplemental Figure 4). This pattern of results was unchanged when computed using modularity to detect these communities, even though the ratios were closer to 1 (mPFC: median = `r round(median(Halves_RIRatios_PFC_Modularity), digits = 2)`, IQR = `r round(quantile(Halves_RIRatios_PFC_Modularity, 0.25), digits = 2)` - `r round(quantile(Halves_RIRatios_PFC_Modularity, 0.75), digits = 2)`; PCC:  median = `r round(median(Halves_RIRatios_PCC_Modularity), digits = 2)`, IQR = `r round(quantile(Halves_RIRatios_PCC_Modularity, 0.25), digits = 2)` - `r round(quantile(Halves_RIRatios_PCC_Modularity, 0.75), digits = 2)`; difference: *p* `r ifelse(Halves_mPFCvPCC_Modularity_permTest$Pval < 0.001, "< 0.001", paste("=", Halves_mPFCvPCC_Modularity_permTest$Pval))`; Cohen's D = `r round(Halves_mPFCvPCC_Modularity_ES, digits = 2)`). We stress that our similarity metric, the ARI, measured the similarity of partitionings in a label-agnostic manner. The greater inter-individual consistency in PCC was therefore not merely an artifact of having used a PCC subregion as the basis for label assignment.

@@

We quantified these observations by dividing the search space into three regions: a ventral mPFC area corresponding to the one used by Lopez-Persem et al. [-@Lopez2019], a superior mPFC zone (sup-mPFC) that contained the remaining dorsal mPFC regions, and PCC (Figure 8B, left). For each individual, we correlated the unthresholded Fiedler vector with cortical curvature for each combination of region and hemisphere. Negative correlations in this context imply that the DN was likely found in sulci and non-DN in gyri. Results can be found on Figure 8B. We found that these features tended to be negatively correlated in both left (mean correlation = `r round(curvStats$meanCor[5], digits = 2)`, SE = `r round(curvStats$seCor[5], digits = 2)`) and right (mean correlation = `r round(curvStats$meanCor[6], digits = 2)`, SE = `r round(curvStats$seCor[6], digits = 2)`) hemispheres of vmPFC across individuals, but this distribution was only significantly different than zero on the right hemisphere (one sample t-test: t = `r curvStats$TStat[6]`, *p* `r ifelse(curvStats$p[6] < 0.001, "< 0.001", paste("=", curvStats$p[6]))`; Cohen's D = `r round(curvStats$ES[6], digits = 2)`). Correlations between FV and curvature were positive and significantly different than zero in both left (mean correlation = `r round(curvStats$meanCor[3], digits = 2)`, SE = `r round(curvStats$seCor[3], digits = 2)`; one sample t-test: t = `r curvStats$TStat[3]`, *p* `r ifelse(curvStats$p[3] < 0.001, "< 0.001", paste("=", curvStats$p[3]))`; Cohen's D = `r round(curvStats$ES[3], digits = 2)`) and right (mean correlation = `r round(curvStats$meanCor[4], digits = 2)`, SE = `r round(curvStats$seCor[4], digits = 2)`; one sample t-test: t = `r curvStats$TStat[4]`, *p* `r ifelse(curvStats$p[4] < 0.001, "< 0.001", paste("=", curvStats$p[4]))`; Cohen's D = `r round(curvStats$ES[4], digits = 2)`) hemispheres of sup-mPFC. Unlike frontal regions, correlations in PCC were negative and significantly different than zero in the left hemisphere (mean correlation = `r round(curvStats$meanCor[1], digits = 2)`, SE = `r round(curvStats$seCor[1], digits = 2)`; one sample t-test: t = `r curvStats$TStat[1]`, *p* `r ifelse(curvStats$p[1] < 0.001, "< 0.001", paste("=", curvStats$p[1]))`; Cohen's D = `r round(curvStats$ES[1], digits = 2)`), but significantly above zero in the right hemisphere (mean correlation = `r round(curvStats$meanCor[2], digits = 2)`, SE = `r round(curvStats$seCor[2], digits = 2)`; one sample t-test: t = `r curvStats$TStat[2]`, *p* `r ifelse(curvStats$p[2] < 0.001, "< 0.001", paste("=", curvStats$p[2]))`; Cohen's D = `r round(curvStats$ES[2], digits = 2)`). The difference across hemispheres was significant (paired t-test: t = `r round(curvPCC_t$statistic, digits = 2`, *p* `r ifelse(curvPCC_t$p.val < 0.001, "< 0.001", paste("=", curvPCC_t$p.val))`; Cohen's D = `r round(curvPCC_ES, digits = 2)`). These results are in line with what can be observed in individual brains, partially replicate the findings from Lopez-Persem et al. [-@Lopez2019], and suggest that the association between function and structure is heterogenous within canonical DN.

@@

Visual inspection of these networks shows high similarity between our DN community and the previously reported sub-network A. However, the non-DN community filled areas not covered by either DN-A or DN-B. Since this three-network configuration is at odds with the two-network solution suggested in our previous analyses (i.e. comparison with modularity), we ran additional evaluations to confirm its existence. First, we reproduced the whole-brain k-means clustering analysis (n of clusters = 12, 100 iterations) performed by Braga et al. [-@Braga2019] in our two subjects using their full time series (Supplemental Figure 5A). In addition to identifying DN networks A and B through this approach (in line with their findings), we found a third cluster that aligned well with the non-DN community. To understand why we could not find this organization before, we performed a silhouette analysis to determine the ideal number of clusters in our search space (Supplemental Figure 5B). For every individual, we ran k-means clusterings with a specified number of clusters ranging from 2 to 5, and computed a silhouette score for each solution (higher silhouette scores indicate a better fit). Scores decreased as the number of clusters increased for all individuals, suggesting that a bisection was indeed the best solution. Paired permutations comparing mean scores across individuals indicated that the difference between two (mean = 0.042, SE = 0.001) and three (mean = 0.032, SE = 0.0009) cluster solutions was significant (*p* < 0.0001, Cohen's D = 0.96). Visualization of a two-cluster k-means revealed a close match with partitionings estimated through modularity, and are comparable to those produced by SP prior to thresholding (Supplemental Figure 5A, bottom rows). These analyses suggest that SP isolated DN-A and the non-DN community as the dominant opposite signals within our search space, but that DN-B is observable once we take advantage of the continuous information contained in the Fiedler vector.

These results supports the idea that the two approaches serve complementary purposes. Whereas Braga and colleagues [-@Braga2017; -@Braga2019] identified subdivisions within the DN, the present community detection approach might be better understood as partitioning DN from non-DN cortex. Furthermore, they show that our approach can identify the three networks in a way that is less computationally demanding than full-brain clustering, outperforming other clustering methods that lack the continuous information provided by SP.

@@

Here we address these challenges by using spectral partitioning (SP), a graph-theoretic community detection algorithm that efficiently separates a network into two [@Fiedler1975; @Higham2007; @Toker2019]. For 100 individuals, we subdivided brain regions that typically show overlap between DN and valuation effects into DN and non-DN communities. Restricting our analyses to a general mPFC/PCC search space made it appropriate to use a technique that identified a vertex-wise, binary partitioning that was sensitive to the complex topography of the brain. This contrasts with whole-brain network analyses, which need to allow for multiple sub-networks and which often use parcels that are several orders of magnitude larger than vertices as the units of analysis. Partitioning an individual's brain network through SP has a number of advantages, including identifying communities deterministically, constraining communities to contain a similar number of vertices (i.e. preventing the allocation of most vertices to a single community), providing continuous values that relate to the strength of a node's community affiliation, and the ability to diagnose the connectedness of a network through examination of its resulting eigenvalues [@chung1997; @Higham2007]. Comparisons with partitionings formed by modularity maximization, which heuristically determines the ideal number of communities [@Garcia2017], suggested the binary partitioning was appropriate.

We found a generalizable pattern across individual partitionings, in which the DN community covered ventral/dorsal mPFC and posterior PCC, with the non-DN community concentrated in pregenual ACC and anterior PCC. The precise spatial positioning of this general community structure was highly heterogenous across individuals, yet stable across test/re-test evaluations within-individual. The idiosyncrasy in functional topography was particularly pronounced in mPFC, and was identified in both run-based and day-based analyses. Individual-specificity could theoretically arise from a variety of sources. For example, the functional topography of mPFC could be governed by its underlying sulcal and gyral organization, which has been shown to vary systematically across individuals [@Mackey2014; @Lopez2019]. Individual variability could also be due to shifts in functional organization that are independent of structural features [@Haxby2013; @Nenning2017], or be characterized by the pattern of functional connections with the rest of the brain [@Mars2018; @Passingham2002; @Tobyne2018]. An important goal for future work will be to assess whether the network layout in this region can be predicted on the basis of aspects of brain structure, such as sulcal morphology, myeloarchitecture [@Glasser2016], or structural connectivity [@Osher2016; @Saygin2011; @Saygin2016].

Network-partitioning methods such as SP are data-driven, and therefore provide no labeling information about the resulting communities. We circumvented this issue by independently identifying the DN community based on its coverage of area 7m, a region in PCC that was preferentially associated with the DN relative to subjective valuation in our meta-analysis. We were able to apply labels derived from this group-level approach on the basis of the topography in PCC, where functional organization was more consistent across individuals. Because each community spanned both mPFC and PCC, the labels extended to mPFC where topography was more heterogeneous.

Our results extend previous work that described individual-specific brain organization. Several recent investigations have identified topographic heterogeneity using a different data aspect ratio than we used here [a small number of individuals and a large number of scanning sessions per individual; @Braga2017; @Braga2019; @Gordon2017]. Previous work has also shown that functional correlations among pre-defined cortical parcels are highly stable within an individual [@Gratton2018b; @Kong2018]. Here we were able to quantify the variability and stability of functional topography in a large sample at a fine, vertex-level spatial granularity, using moderately low amounts of data (down to a single 14 minute scan). The motivation to sub-divide DN also stems from recent work by Kernbach et al. [-@Kernbach2018], which identified specialized communication of parcels within DN with the rest of the brain in a large pool of individuals.

@@

The community organization of PCC and mPFC was congruent with DN sub-networks A and B proposed by Braga & Buckner [-@Braga2017; @Braga2019]. The topography of our thresholded DN community closely matched network A, whereas our non-DN community included cortical territory that was not part of either DN network. Subthreshold vertices from the DN community overlapped with DN-B vertices, suggesting that this sub-network could act as a dynamic intermediary between DN-A and other networks. Our findings therefore complement the initial identification of DN sub-networks by quantifying the systematic variability of their underlying topography in a larger group of people. Understanding the interaction of networks A (DN), B, and non-DN is an important goal for future research. These two sets of results collectively suggest that canonical DN regions can be topographically partitioned into DN and non-DN communities, and that the DN community can in turn be further divided into sub-networks A and B.

Our findings show that the functional topography of mPFC is variable across a large pool of individuals, and that the SP algorithm is a useful tool for identifying individualized topography in a data-driven way. The ability to capture an individual's functional topography without the need of group priors is clinically relevant, as it could help characterize heterogenous changes in mPFC activity in disorders such as depression and schizophrenia [@Hiser2018]. It will be beneficial for future task-based fMRI experiments to be able to characterize where task-evoked activity is situated relative to an individual's overall mPFC organization. Our work was originally motivated by the apparent spatial overlap between subjective valuation and the default network [@Acikalin2017], but additional distinctions of interest include valuation versus episodic memory functions [@Euston2012], self-referential thought and theory of mind [@Mitchell2005], and potential topographic distinctions among multiple forms of valuation [@Clithero2014; @Shenhav2019; @Smith2010]. An individualized frame of reference will enhance the ability of future studies to gauge similarities and differences among brain activity patterns associated with diverse psychological domains.

>>>>

---
title: Individual heterogeneity in the functional network topography of medial prefrontal
  cortex
author: "Claudio Toro-Serey^1^, Sean M. Tobyne^2^, & Joseph T. McGuire^1^"
csl: apa.csl
output:
  pdf_document:
    highlight: haddock
    keep_tex: no
  word_document: #default
    reference_docx: Style_reference_draft.docx
header-includes:
- \usepackage{setspace}\doublespacing
- \usepackage[left]{lineno}
- \linenumbers
- \usepackage{float}
- \newcommand{\beginsupplement}{ \setcounter{table}{0} \renewcommand{\thetable}{S\arabic{table}}
  \setcounter{figure}{0} \renewcommand{\thefigure}{S\arabic{figure}} }
subtitle: 'Abbreviated Title: Heterogeneity in the functional topography of mPFC'
bibliography: mPFC_paper.bib
---

@@

@@

  The outline of our paper is as follows. First, we established a search space by selecting parcels from an established brain atlas [@Glasser2016] that corresponded to previously defined DN and limbic networks on the medial cortical wall [@Yeo2011]. A cortical surface-based meta-analysis of the DN and valuation literatures identified a parcel in PCC that was DN-specific at the aggregate level. We then derived a functional connectivity network of all the surface vertices within the search space for each of `r length(dir(path = './Summary'))` individual resting-state fMRI data sets from the Human Connectome Project [HCP; @VanEssen2012], and used the SP algorithm to subdivide each individual's network into DN and non-DN communities (labeled according to which community included the meta-analytically identified DN-specific parcel in PCC). Focusing on individual vertices in the search space rather than the parcels (as is typical in brain network analyses) allowed us to finely delineate the topographic extent of each community. The resulting communities varied topographically across individuals, while also appearing to follow common organizational principles. Sliding window and test-retest analyses showed that these partitionings were highly similar across scanning days within (but not between) individuals, and that individual-level idiosyncrasy was greater in mPFC. Partitionings obtained from the SP algorithm had higher test-retest reliability than did analogous results from seed-based functional connectivity. We found that the DN community was likely to be located within principal sulci in ventral mPFC and left PCC, but in gyri within superior mPFC and right PCC. Lastly, we describe how the structure of the resulting automatically defined DN and non-DN communities both aligns with and differs from a recently proposed scheme for identifying subdivisions within the DN [@Braga2017; @Braga2019]. Our work highlights the usefulness of estimating brain effects at the individual level in mPFC and PCC, provides a new framework and tool set for future investigations of overlap across cognitive domains, and motivates future re-examination of seemingly inseparable cognitive processes (such as valuation and introspective thought) in these areas.

@@

Figure 2 shows a representative partitioning of the search space for a single participant (100307; additional examples are presented in the first two columns of Supplemental Figure 1). The SP algorithm subdivides a network according to the positive versus negative values in the Fiedler vector (the eigenvector related to the second-to-lowest eigenvalue of the network's normalized Laplacian matrix, see Methods). Since this is a data-driven approach, there is no a priori labeling for the two communities. We assigned the DN label to the community that contained the DN-specific PCC parcel from the meta-analysis (7m). We oriented each individual's Fiedler vector so positive values corresponded to the DN community [@Nenning2017], and were assigned a value of 1 in the binarized partitionings (with 0 denoting non-DN). In qualitative terms, the resulting patterns contained substantial DN coverage in posterior PCC (as dictated by our labeling strategy), with non-DN vertices in anterior PCC. The mPFC region tended to include DN vertices in its ventral-anterior and dorsal-anterior areas, with a persistent non-DN pocket between them. This non-DN section extended posteriorly into pregenual cinglate cortex (area a24). We note that the addition of restrosplenial cortex (an area commonly regarded as part of canonical DN) to the search space did not change these results, and that the area was adequately covered by the DN community (Supplemental Figure 1).

@@

Figure 6 shows ARI ratios for PCC and mPFC. A signed-rank test showed evidence for specificity (i.e. ratios > 1) in both mPFC (median = `r round(median(Halves_RIRatios_PFC), digits = 2)`, IQR = `r round(quantile(Halves_RIRatios_PFC, 0.25), digits = 2)` - `r round(quantile(Halves_RIRatios_PFC, 0.75), digits = 2)`, V = `r Halves_PFC_ratioTest$statistic`, *p* `r ifelse(Halves_PFC_ratioTest$p.value < 0.001, "< 0.001", paste("=", Halves_PFC_ratioTest$p.value))`) and PCC (median = `r round(median(Halves_RIRatios_PCC), digits = 2)`, IQR = `r round(quantile(Halves_RIRatios_PCC, 0.25), digits = 2)` - `r round(quantile(Halves_RIRatios_PCC, 0.75), digits = 2)`, V = `r Halves_PCC_ratioTest$statistic`, *p* `r ifelse(Halves_PCC_ratioTest$p.value < 0.001, "< 0.001", paste("=", Halves_PCC_ratioTest$p.value))`). Moreover, the ratios for mPFC were significantly greater than those for PCC when compared with a paired permutation test (*p* `r ifelse(Halves_mPFCvPCC_permTest$Pval < 0.001, "< 0.001", paste("=", Halves_mPFCvPCC_permTest$Pval))`; Cohen's D = `r round(Halves_mPFCvPCC_ES, digits = 2)`). This pattern was mostly unchanged when computed using modularity to detect these communities, showing that the results persist even without a forced binarization (mPFC: median = `r round(median(Halves_RIRatios_PFC_Modularity), digits = 2)`, IQR = `r round(quantile(Halves_RIRatios_PFC_Modularity, 0.25), digits = 2)` - `r round(quantile(Halves_RIRatios_PFC_Modularity, 0.75), digits = 2)`; PCC:  median = `r round(median(Halves_RIRatios_PCC_Modularity), digits = 2)`, IQR = `r round(quantile(Halves_RIRatios_PCC_Modularity, 0.25), digits = 2)` - `r round(quantile(Halves_RIRatios_PCC_Modularity, 0.75), digits = 2)`; difference: *p* `r ifelse(Halves_mPFCvPCC_Modularity_permTest$Pval < 0.001, "< 0.001", paste("=", Halves_mPFCvPCC_Modularity_permTest$Pval))`; Cohen's D = `r round(Halves_mPFCvPCC_Modularity_ES, digits = 2)`). These test/retest results suggest that the topographic variability seen in mPFC arises at least in part from stable and subject-specific organizational patterns (examples of these partitionings can be found on Supplemental Figure 4). We stress that our similarity metric, the ARI, measured the similarity of partitionings in a label-agnostic manner. The greater inter-individual consistency in PCC was therefore not merely an artifact of having used a PCC subregion as the basis for label assignment.

@@

We quantified these observations by dividing the search space into three regions: a ventral mPFC area corresponding to the one used by Lopez-Persem et al. [-@Lopez2019], a superior mPFC zone (sup-mPFC) that contained the remaining dorsal mPFC regions, and PCC (Figure 8B, left). For each individual, we correlated the unthresholded Fiedler vector with cortical curvature for each combination of region and hemisphere. Negative correlations in this context imply that the DN was likely found in sulci and non-DN in gyri. Results can be found on Figure 8B. We found that these features tended to be negatively correlated in both left (mean correlation = `r round(curvStats$meanCor[5], digits = 2)`, SE = `r round(curvStats$seCor[5], digits = 2)`) and right (mean correlation = `r round(curvStats$meanCor[6], digits = 2)`, SE = `r round(curvStats$seCor[6], digits = 2)`) hemispheres of vmPFC across individuals, but this distribution was only significantly different than zero on the right hemisphere (one sample t-test: t = `r curvStats$TStat[6]`, *p* `r ifelse(curvStats$p[6] < 0.001, "< 0.001", paste("=", curvStats$p[6]))`; Cohen's D = `r round(curvStats$ES[6], digits = 2)`). Correlations between FV and curvature were positive and significantly different than zero in both left (mean correlation = `r round(curvStats$meanCor[3], digits = 2)`, SE = `r round(curvStats$seCor[3], digits = 2)`; one sample t-test: t = `r curvStats$TStat[3]`, *p* `r ifelse(curvStats$p[3] < 0.001, "< 0.001", paste("=", curvStats$p[3]))`; Cohen's D = `r round(curvStats$ES[3], digits = 2)`) and right (mean correlation = `r round(curvStats$meanCor[4], digits = 2)`, SE = `r round(curvStats$seCor[4], digits = 2)`; one sample t-test: t = `r curvStats$TStat[4]`, *p* `r ifelse(curvStats$p[4] < 0.001, "< 0.001", paste("=", curvStats$p[4]))`; Cohen's D = `r round(curvStats$ES[4], digits = 2)`) hemispheres of sup-mPFC. Unlike frontal regions, correlations in PCC were negative and significantly different than zero in the left hemisphere (mean correlation = `r round(curvStats$meanCor[1], digits = 2)`, SE = `r round(curvStats$seCor[1], digits = 2)`; one sample t-test: t = `r curvStats$TStat[1]`, *p* `r ifelse(curvStats$p[1] < 0.001, "< 0.001", paste("=", curvStats$p[1]))`; Cohen's D = `r round(curvStats$ES[1], digits = 2)`), but significantly above zero in the right hemisphere (mean correlation = `r round(curvStats$meanCor[2], digits = 2)`, SE = `r round(curvStats$seCor[2], digits = 2)`; one sample t-test: t = `r curvStats$TStat[2]`, *p* `r ifelse(curvStats$p[2] < 0.001, "< 0.001", paste("=", curvStats$p[2]))`; Cohen's D = `r round(curvStats$ES[2], digits = 2)`). The difference across hemispheres was significant (paired t-test: t = `r round(curvPCC_t$statistic, digits = 2)`, *p* `r ifelse(curvPCC_t$p.val < 0.001, "< 0.001", paste("=", curvPCC_t$p.val))`; Cohen's D = `r round(curvPCC_ES, digits = 2)`). These results are in line with what can be observed in individual brains, partially replicate the findings from Lopez-Persem et al. [-@Lopez2019], and suggest that the association between function and structure is heterogenous within canonical DN.

@@

Visual inspection of these networks shows high similarity between our DN community and the previously reported sub-network A. However, the non-DN community filled areas not covered by either DN-A or DN-B. Since this three-network configuration is at odds with the two-network solution suggested in our previous analyses (i.e. comparison with modularity), we ran additional evaluations to confirm its existence. First, we reproduced the whole-brain k-means clustering analysis (n of clusters = 12, 100 iterations) performed by Braga et al. [-@Braga2019] in our two subjects using their full time series (Supplemental Figure 5A). In addition to identifying DN networks A and B through this approach (in line with their findings), we found a third cluster that aligned well with the non-DN community. To understand why we could not find the three discrete clusters before, we performed a silhouette analysis to determine the ideal number of clusters in our search space (Supplemental Figure 5B). For every individual, we ran k-means clusterings with a specified number of clusters ranging from 2 to 5, and computed a silhouette score for each solution (higher silhouette scores indicate a better fit). Scores decreased as the number of clusters increased for all individuals, suggesting that a bisection was indeed the best solution. Paired permutations comparing mean scores across individuals indicated that the difference between two (mean = 0.042, SE = 0.001) and three (mean = 0.032, SE = 0.0009) cluster solutions was significant (*p* < 0.0001, Cohen's D = 0.96). Visualization of a two-cluster k-means revealed a close match with partitionings estimated through modularity, and are comparable to those produced by SP prior to thresholding (Supplemental Figure 5A, bottom rows). These analyses suggest that SP isolated DN-A and the non-DN community as the dominant opposite signals within our search space, but that DN-B is observable once we take advantage of the continuous information contained in the Fiedler vector.

These results supports the idea that the two approaches serve complementary purposes. Whereas Braga and colleagues [-@Braga2017; -@Braga2019] identified subdivisions within the DN, the present community detection approach might be better understood as partitioning DN from non-DN cortex. Furthermore, they show that our approach can identify the three networks in PCC and mPFC in a way that is less computationally demanding than full-brain clustering, outperforming other clustering methods that lack the type of continuous information provided by SP.

@@

Here we address these challenges by using spectral partitioning (SP), a graph-theoretic community detection algorithm that efficiently separates a network into two [@Fiedler1975; @Higham2007; @Toker2019]. For 100 individuals, we subdivided brain regions that typically show overlap between DN and valuation effects into DN and non-DN communities. Restricting our analyses to a general mPFC/PCC search space made it appropriate to use a technique that identified a vertex-wise, binary partitioning that was sensitive to the complex topography of the brain. This contrasts with whole-brain network analyses, which need to allow for multiple sub-networks and which often use parcels that are several orders of magnitude larger than vertices as the units of analysis. Partitioning an individual's brain network through SP has a number of advantages, including identifying communities deterministically, constraining communities to contain a similar number of vertices (i.e. preventing the allocation of most vertices to a single community), providing continuous values that relate to the strength of a node's community affiliation, and the ability to diagnose the connectedness of a network through examination of its resulting eigenvalues [@chung1997; @Higham2007]. Comparisons with partitionings formed by modularity maximization, which heuristically determines the ideal number of communities [@Garcia2017], plus a silhouette analysis, suggested the binary partitioning was appropriate.

We found a generalizable pattern across individual partitionings, in which the DN community covered ventral/dorsal mPFC and posterior PCC, with the non-DN community concentrated in pregenual ACC and anterior PCC. The precise spatial positioning of this general community structure was highly heterogenous across individuals, yet stable across test/re-test evaluations within-individual. The idiosyncrasy in functional topography was particularly pronounced in mPFC, and was identified in both run-based and day-based analyses. Individual-specificity could theoretically arise from a variety of sources. For example, Individual variability could be due to shifts in functional organization that are independent of structural features [@Haxby2013; @Nenning2017], or be characterized by the pattern of functional connections with the rest of the brain [@Mars2018; @Passingham2002; @Tobyne2018]. Alternatively, the functional topography of mPFC could be governed by its underlying sulcal and gyral organization, which has been shown to vary systematically across individuals [@Mackey2014]. Our findings support this idea, echoing previous findings that DN is contained within sulci (in particular the superior rostral sulcus) in vmPFC [@Lopez2019]. This relationship was heterogeneous throughout the rest of the search space, as more dorsal mPFC regions were likely located in gyri, whereas PCC had hemispheric differences in this association.  An important goal for future work will be to assess whether the network layout in these regions can also be predicted on the basis of other aspects of brain structure, such as myeloarchitecture [@Glasser2016] or structural connectivity [@Osher2016; @Saygin2011; @Saygin2016].

Network-partitioning methods such as SP are data-driven, and therefore provide no labeling information about the resulting communities. We circumvented this issue by independently identifying the DN community based on its coverage of area 7m, a region in PCC that was preferentially associated with the DN relative to subjective valuation in our meta-analysis. Our focus on this contrast was approapriate because of the notable topographical overlap between these processes in mPFC and PCC, despite being segregable elsewhere in the brain [@Acikalin2017]. We were able to apply labels derived from this group-level approach on the basis of the topography in PCC, where functional organization was more consistent across individuals. Because each community spanned both mPFC and PCC, the labels extended to mPFC where topography was more heterogeneous.

Our results extend previous work that described individual-specific brain organization. Several recent investigations have identified topographic heterogeneity using a different data aspect ratio than we used here [a small number of individuals and a large number of scanning sessions per individual; @Braga2017; @Braga2019; @Gordon2017]. Previous work has also shown that functional correlations among pre-defined cortical parcels are highly stable within an individual [@Gratton2018b; @Kong2018]. Here we were able to quantify the variability and stability of functional topography in a large sample at a fine, vertex-level spatial granularity, using moderately low amounts of data (down to a single 14 minute scan, although estimates become considerably more unreliable). The motivation to sub-divide DN also stems from recent work by Kernbach et al. [-@Kernbach2018], which identified specialized communication of parcels within DN with the rest of the brain in a large pool of individuals.

@@

The community organization of PCC and mPFC was congruent with DN sub-networks A and B proposed by Braga & Buckner [-@Braga2017; @Braga2019]. The topography of our thresholded DN community closely matched network A, whereas our non-DN community included cortical territory that was not part of either DN network. Subthreshold vertices from the SP communities in turn overlapped with DN-B vertices. Our findings therefore complement the initial identification of DN sub-networks by quantifying the systematic variability of their underlying topography in a larger group of people. Understanding the interaction of networks A (DN), B, and non-DN is an important goal for future research. SP is related to methods that have gained traction recently for distinguishing functional cortical gradients [@Margulies2016; @Huntenburg2018]. Dedicated work could determine whether DN-A and DN-B form part of a gradual information processing sequence, or if their functions can be discretized. Regardless, this set of results collectively suggest that canonical DN regions can be topographically partitioned into DN and non-DN communities, and that the DN community can in turn be further divided into sub-networks A and B.

Our findings show that the functional topography of mPFC is variable across a large pool of individuals, and that the SP algorithm is a useful tool for identifying individualized topography in a data-driven way. The ability to capture an individual's functional topography without the need of group priors is clinically relevant, as it could help characterize heterogenous changes in mPFC activity in disorders such as depression and schizophrenia [@Hiser2018]. It will be beneficial for future task-based fMRI experiments to be able to characterize where task-evoked activity is situated relative to an individual's overall mPFC organization. Our work was originally motivated by the apparent spatial overlap between subjective valuation and the default network [@Acikalin2017], but additional distinctions of interest include valuation versus episodic memory functions [@Euston2012], self-referential thought and theory of mind [@Mitchell2005], which have been grouped under the DN umbrella based on group averages [@Spreng2012], and potential topographic distinctions among multiple forms of valuation [@Clithero2014; @Shenhav2019; @Smith2010]. An individualized frame of reference will enhance the ability of future studies to gauge similarities and differences among brain activity patterns associated with diverse psychological domains.
